A general Nullstellensatz for generalized spaces

### 2019-03-13 paper-qcoh.tex
Remark on explicitness of characterization

>>>>

Theorem~\ref{thm:characterization0} characterizes which first-order formulas
hold for the generic model. We could of course wish for a more explicit
characterization; but since even the characterization of geometric sequents
holding for the generic model (they are precisely those which are provable in
geometric logic modulo~$\TT$) is of a rather implicit nature, this wish appears
unfounded.

We stress that our characterization is more explicit than the tautologous
characterization (``a first-order formula holds for~$U_\TT$ iff it is provable
in~$\TT'$, where~$\TT'$ is the first-order theory whose set of axioms is the
set of first-order formulas satisfied by~$U_\TT$'') and the (incorrect)
characterization ``a first-order formula holds for~$U_\TT$ iff it
is~$\TT$-redundant''. Indeed, if~$\TT$ happens to be coherent and recursively
axiomatizable, then in stating Theorem~\ref{thm:characterization0} we may
restrict to coherent existential fixed-point logic, and the resulting theory
will again be recursively axiomatizable.
\medskip
